---
title: "Integrated Discrete Environmental Analytics System"
author: "Chiranjib Chaudhuri"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = './doc/Figure/')
```

## GitHub Documents

This document explains the analytic capabilities of the IDEAS data model. 

```{r libraries and connection, echo=FALSE}
library(DBI)
library(dplyr)
library(sf)
con = dbConnect(RNetezza::Netezza(), dsn='NZSQL')
```
We connect to a table containing spatial-time series of annual extreme daily climate variables for entire Canada. 

```{r Loading Data, echo=FALSE}
data=tbl(con,"ANUSPLINE3")
head(data)
```
Next we slice the data set for annual maximum daily precipitation. 
```{r Slice data, echo=FALSE}
datap=data%>%filter(KEY=='PRECIPITATION')
head(datap)
```
We will calculate time-series of spatial average

```{r Temporal Analysis, echo=FALSE}
avgs=datap%>%group_by(TID)%>%arrange(TID)%>%summarise(VALUE=mean(VALUE))
head(avgs)
```
We will calculate spatial distribution of temporal average

```{r Spatial Analysis, echo=FALSE}
avgt=datap%>%group_by(DGGID)%>%arrange(DGGID)%>%summarise(VALUE=mean(VALUE))
head(avgt)
```

Let us plot some of these basic variables. 

```{r Time-series Plots, echo=FALSE}
avgs=collect(avgs)
plot(avgs$TID,avgs$VALUE)
```
To plot the spatial variable we need to attach it with the spatial tabls.
```{r Connect grid, echo=FALSE}
grid=tbl(con,"FINALGRID2")
head(grid)
```

```{r Spatial Plots, echo=FALSE}
avgt=avgt%>%inner_join(grid,by=c('DGGID'))%>%mutate(WKT=inza..ST_AsText(GEOM))%>%
  select(DGGID,VALUE,WKT)%>%arrange(DGGID)%>%head(100)%>%collect()

poly=st_as_sf(avgt, wkt='WKT', crs = 4326)
plot(poly['VALUE'])
```

Lets get a little more complex now. We want to clip the data for one of the eco-zone over Canada say somwhere over BC, Pacific-Maritime (ecozone=13)
```{r Connect ecozone, echo=FALSE}
ecozone=tbl(con,"ECOZONE_12")%>%filter(VALUE==13)%>%select(DGGID)
head(ecozone)
```
```{r Clip to ecozone, echo=FALSE}
datape=datap%>%inner_join(ecozone,by=c('DGGID'))
head(datape)
```




