---
title: "Spatial Overlay in IDEAS"
author: "C. Robertson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Tutorial Overview

This tutorial demonstrates some simple spatial overlay analysis of polygon data using the `IDEAS` data model, as described in [Robertson et al. 2020.](https://www.sciencedirect.com/science/article/pii/S0924271620300502)

## Preliminaries

We will load some sample data from the  `stampr` package, and pull out two polygons to demonstrate overlay operations.

```{r message=FALSE, warning=FALSE}
library(stampr)
library(sp)
data(mpb)
P1 <- subset(mpb, TGROUP==1)[5,]
P2 <- subset(mpb, TGROUP==2)[7,]
plot(P2, border="green")
plot(P1, add=TRUE, border="blue")
```

First we need to load some libraries;
```{r message=FALSE, warning=FALSE}
library("dplyr")
library("dbplyr")
library("DBI")
library("leaflet")
library("sf")
library("RODBC")
library("nzdggs")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
Sys.setenv(ODBCINI="/usr/local/etc/odbc.ini")
Sys.setenv(NZ_ODBC_INI_PATH="/usr/local/etc/")
con = dbConnect(RNetezza::Netezza(), dsn='NZSQL')
#conw = odbcConnect('NZSQLF')
```

## Loading Polygon Data from IDEAS
We will use the `con` data connection to access a table called `mpb` which has the same data from the `stampr` package in `IDEAS` format.

```{r message=FALSE, warning=FALSE}
mpb.i <- tbl(con,"MPB")
grid <- tbl(con,"FINALGRID2") %>% filter(RESOLUTION==19)
head(mpb.i)
```

We want to pull out those same two polygons by identifying them by their ID values, as follows:
```{r message=FALSE, warning=FALSE}
ID1 <- P1$ID
ID2 <- P2$ID
 
P1.i <- mpb.i %>% filter(KEY=="ID") %>% filter(VALUE==ID1) %>% inner_join(., grid, "DGGID") %>% mutate(WKT=inza..ST_AsText(GEOM)) %>% collect()
P2.i <- mpb.i %>% filter(KEY=="ID") %>% filter(VALUE==ID2) %>% inner_join(., grid, "DGGID") %>% mutate(WKT=inza..ST_AsText(GEOM)) %>% collect() 

dbDisconnect(con)

plot(st_as_sf(P2.i, wkt='WKT', crs = 4326)['TID'], col='green', reset=FALSE)
plot(st_as_sf(P1.i, wkt='WKT', crs = 4326)['TID'], add=TRUE, col='blue')
```

## Overlay Analysis using `IDEAS` data model
### Intersection
```{r message=FALSE, warning=FALSE}

intersection <- P1.i %>% inner_join(., P2.i, "DGGID")
plot(st_as_sf(P2.i, wkt='WKT', crs = 4326)['TID'], col='green', reset=FALSE)
plot(st_as_sf(P1.i, wkt='WKT', crs = 4326)['TID'], add=TRUE, col='blue')
plot(st_as_sf(intersection, wkt='WKT.x', crs = 4326)['TID.x'], add=TRUE, col='red')
```

### Union
```{r message=FALSE, warning=FALSE}
union <- union_all(P1.i, P2.i) %>% distinct(DGGID, .keep_all = TRUE)
plot(st_as_sf(union, wkt=c('WKT'), crs = 4326)['TID'], col='red')
```

### A NOT B
```{r message=FALSE, warning=FALSE}
ANotB <- P1.i %>% anti_join(., P2.i, "DGGID")
plot(st_as_sf(P2.i, wkt='WKT', crs = 4326)['TID'], col='green', reset=FALSE)
plot(st_as_sf(ANotB, wkt=c('WKT'), crs = 4326)['TID'], add=TRUE, col='red')
```

